### 2019-03-15 ChapitresPFE/k2_trees/SynK2.tex

														\begin{landscape}
								\begin{table}
									\begin{tabular}{|C{3cm}|c|c|c|c|c|c|c|c|c|c|c|c|c|}
										\hline
										\multirow{2}{*}[-25pt]{     Article   }  & \multicolumn{5}{c|}{Graphe en entrée} & \multicolumn{2}{c|}{Compression} & \multicolumn{2}{c|}{Structure en sortie} & \multirow{2}{*}[-25pt]{Graphe de test} & \multirow{2}{*}[-25pt]{Résultat }  \\ \cline{2-10}
				     & \rotatebox[origin=c]{90}{ Orienté }  & \rotatebox[origin=c]{90}{ Non orienté } & \rotatebox[origin=c]{90}{ Statique } & \rotatebox[origin=c]{90}{ Dynamique } & \rotatebox[origin=c]{90}{ Autre Propriétés } &  \rotatebox[origin=c]{90}{ Avec perte } & \rotatebox[origin=c]{90}{ Sans perte } & \rotatebox[origin=c]{90}{ Succincte } & \rotatebox[origin=c]{90}{ Structurelle } & & \\ \hline				%%%%%%Fin du header

@@

	cond-mat
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.4\textwidth}
	 5.21 bits/lien \\
	 taux de compression : 16.88\% \\
	 taux de compression : 15.58\% 
  \end{minipage}	\\

\hline $k^2$-trees : Hybridation \citep{brisaboa2009k} & \cmark & \cmark & \cmark & \xmark &  & \xmark &  \cmark & \cmark & \xmark  & 
										\begin{minipage}[t]{0.15\textwidth}
	eu-2005
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.4\textwidth}
	 5.21 bits/lien 
  \end{minipage}	\\  
\hline $k^2$-trees : Optimisation \citep{shi2012optimizing} & \cmark & \cmark & \cmark & \xmark &  & \xmark &  \cmark & \cmark & \xmark  & 
\begin{minipage}[t]{0.15\textwidth}
	cond-mat
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.4\textwidth}

	 taux de compression : 37.96\% 
  \end{minipage}	\\
  			\hline

\hline $k^2$-trees : Amélioration \citep{brisaboa2014compact} & \cmark & \cmark & \cmark & \xmark &  & \xmark &  \cmark & \cmark & \xmark  & 
  				\begin{minipage}[t]{0.15\textwidth}
	eu-2005
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.4\textwidth}

@@

\hline d$k^2$-trees \citep{brisaboa2012compressed} & \cmark & \cmark & \xmark & \cmark &  & \xmark &  \cmark & \cmark & \xmark  &
  				\begin{minipage}[t]{0.15\textwidth}
	eu-2005
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.4\textwidth}

@@

\hline $k^n$-trees \citep{de2013compact} & \cmark & \cmark & \xmark & \cmark & & \xmark & \cmark & \cmark & \xmark  &
  				\begin{minipage}[t]{0.15\textwidth}
	CommNet
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.4\textwidth}

	 taux de compression : 65.16\% 
  \end{minipage}	\\
  \hline

@@

%% deuxiéme tableau

					\begin{landscape}
								\begin{table}
									\begin{tabular}{|C{3cm}|c|c|c|c|c|c|c|c|c|c|c|c|c|}
										\hline
										\multirow{2}{*}[-25pt]{Article}  & \multicolumn{5}{c|}{Graphe en entrée} & \multicolumn{2}{c|}{Compression} & \multicolumn{2}{c|}{Structure en sortie} & \multirow{2}{*}[-25pt]{Graphe de test} & \multirow{2}{*}[-25pt]{Résultat }  \\ \cline{2-10}
				& \rotatebox[origin=c]{90}{ Orienté }  & \rotatebox[origin=c]{90}{ Non orienté } & \rotatebox[origin=c]{90}{ Statique } & \rotatebox[origin=c]{90}{ Dynamique } & \rotatebox[origin=c]{90}{ Autre Propriétés } &  \rotatebox[origin=c]{90}{ Avec perte } & \rotatebox[origin=c]{90}{ Sans perte } & \rotatebox[origin=c]{90}{ Succincte } & \rotatebox[origin=c]{90}{ Structurelle } & & \\ \hline				%%%%%%Fin du header

\hline $k^2$-trees1\citep{de2014new} & \cmark & \cmark & \cmark & \xmark & & \xmark & \cmark & \cmark & \xmark  & 
  							\begin{minipage}[t]{0.1\textwidth}
	eu-2005
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.35\textwidth}
	 taux de compression : 16.23\% 
  \end{minipage}	\\
  \hline

\hline Delta-$k^2$-trees  \citep{zhang2014delta} & \cmark & \cmark & \cmark & \xmark & & \xmark & \cmark & \cmark & \xmark  & 
  							\begin{minipage}[t]{0.1\textwidth}
	eu-2005
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.35\textwidth}
	 3.24 bits/lien 
  \end{minipage}	\\
  \hline

\hline $k^2$-treaps  \citep{brisaboa2014k} & \cmark & \cmark & \cmark & \xmark & 
\begin{minipage}[t]{0.15\textwidth}
  			Pondéré 
  \end{minipage}		
   & \xmark & \cmark & \cmark & \xmark  & 
  							\begin{minipage}[t]{0.1\textwidth}
	SalesDay
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.35\textwidth}
	 2.48 bits/lien
  \end{minipage}	\\
  \hline

\hline I$k^2$-trees  \citep{garcia2014interleaved} & \cmark & \cmark & \xmark & \cmark & & \xmark & \cmark & \cmark & \xmark  & 
  							\begin{minipage}[t]{0.1\textwidth}
	CommNet
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.35\textwidth}

	 taux de compression : 60.43\% 
  \end{minipage}	\\
  \hline

\hline Diff I$k^2$-trees  \citep{alvarez2017succinct} & \cmark & \cmark & \xmark & \cmark & & \xmark & \cmark & \cmark & \xmark  & 
  							\begin{minipage}[t]{0.1\textwidth}
	CommNet
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.35\textwidth}

	 taux de compression : 60.43\% 
  \end{minipage}	\\
  \hline

\hline Att $k^2$-trees  \citep{alvarez2018compact} & \cmark & \cmark & \cmark & \xmark & 
\begin{minipage}[t]{0.1\textwidth}
  			Étiqueté\\
  			Attribué\\
  			Multiple
  \end{minipage}	
& \xmark & \cmark & \cmark & \xmark  & 
  							\begin{minipage}[t]{0.15\textwidth}
	Movielen-10M
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.35\textwidth}

	 taux de compression : 89.97\% 
  \end{minipage}	\\
  \hline

\hline dynAtt $k^2$-trees  \citep{alvarez2018compact} & \cmark & \cmark & \xmark & \cmark & 
\begin{minipage}[t]{0.1\textwidth}
  			Étiqueté\\
  			Attribué\\
  			Multiple
  \end{minipage}	
& \xmark & \cmark & \cmark & \xmark  & 
			\begin{minipage}[t]{0.1\textwidth}
	Movielen-10M
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.35\textwidth}

	 taux de compression : 93.75\% 
  \end{minipage}	\\  				
  				\hline

>>>>

														\begin{landscape}
								\begin{table}
									\begin{tabular}{|C{6cm}|c|c|c|c|c|c|c|c|c|c|c|c|c|}
										\hline
										\multirow{2}{*}[-25pt]{     Article   }  & \multicolumn{5}{c|}{Graphe en entrée} & \multicolumn{2}{c|}{Compression} & \multicolumn{2}{c|}{Structure en sortie} & \multirow{2}{*}[-25pt]{Graphe de test} & \multirow{2}{*}[-25pt]{Résultat}  \\ \cline{2-10}
				     & \rotatebox[origin=c]{90}{ Orienté }  & \rotatebox[origin=c]{90}{ Non orienté } & \rotatebox[origin=c]{90}{ Statique } & \rotatebox[origin=c]{90}{ Dynamique } & \rotatebox[origin=c]{90}{ Autre Propriétés } &  \rotatebox[origin=c]{90}{ Avec perte } & \rotatebox[origin=c]{90}{ Sans perte } & \rotatebox[origin=c]{90}{ Succincte } & \rotatebox[origin=c]{90}{ Structurelle } & & \\ \hline				%%%%%%Fin du header

@@

	cond-mat
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.2\textwidth}
	 5.21 bits/lien \\
	 16.88\% \\
	 15.58\% 
  \end{minipage}	\\

\hline $k^2$-trees : Hybridation \citep{brisaboa2009k} & \cmark & \cmark & \cmark & \xmark &  & \xmark &  \cmark & \cmark & \xmark  & 
										\begin{minipage}[t]{0.15\textwidth}
	eu-2005
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.2\textwidth}
	 5.21 bits/lien 
  \end{minipage}	\\  
\hline $k^2$-trees : Optimisation \citep{shi2012optimizing} & \cmark & \cmark & \cmark & \xmark &  & \xmark &  \cmark & \cmark & \xmark  & 
\begin{minipage}[t]{0.15\textwidth}
	cond-mat
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.2\textwidth}

	 37.96\% 
  \end{minipage}	\\
  			\hline

\hline $k^2$-trees : Amélioration \citep{brisaboa2014compact} & \cmark & \cmark & \cmark & \xmark &  & \xmark &  \cmark & \cmark & \xmark  & 
  				\begin{minipage}[t]{0.15\textwidth}
	eu-2005
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.2\textwidth}

@@

\hline d$k^2$-trees \citep{brisaboa2012compressed} & \cmark & \cmark & \xmark & \cmark &  & \xmark &  \cmark & \cmark & \xmark  &
  				\begin{minipage}[t]{0.15\textwidth}
	eu-2005
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.2\textwidth}

@@

\hline $k^n$-trees \citep{de2013compact} & \cmark & \cmark & \xmark & \cmark & & \xmark & \cmark & \cmark & \xmark  &
  				\begin{minipage}[t]{0.15\textwidth}
	CommNet
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.2\textwidth}

	 65.16\% 
  \end{minipage}	\\
  \hline

\hline $k^2$-trees1\citep{de2014new} & \cmark & \cmark & \cmark & \xmark & & \xmark & \cmark & \cmark & \xmark  & 
  							\begin{minipage}[t]{0.1\textwidth}
	eu-2005
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.2\textwidth}
	 16.23\% 
  \end{minipage}	\\
  \hline

\hline Delta-$k^2$-trees  \citep{zhang2014delta} & \cmark & \cmark & \cmark & \xmark & & \xmark & \cmark & \cmark & \xmark  & 
  							\begin{minipage}[t]{0.1\textwidth}
	eu-2005
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.2\textwidth}
	 3.24 bits/lien 
  \end{minipage}	\\
  \hline

\hline $k^2$-treaps  \citep{brisaboa2014k} & \cmark & \cmark & \cmark & \xmark & 
\begin{minipage}[t]{0.15\textwidth}
  			Pondéré 
  \end{minipage}		
   & \xmark & \cmark & \cmark & \xmark  & 
  							\begin{minipage}[t]{0.1\textwidth}
	SalesDay
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.2\textwidth}
	 2.48 bits/lien
  \end{minipage}	\\
  \hline

\hline I$k^2$-trees  \citep{garcia2014interleaved} & \cmark & \cmark & \xmark & \cmark & & \xmark & \cmark & \cmark & \xmark  & 
  							\begin{minipage}[t]{0.1\textwidth}
	CommNet
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.2\textwidth}

	 60.43\% 
  \end{minipage}	\\
  \hline

\hline Diff I$k^2$-trees  \citep{alvarez2017succinct} & \cmark & \cmark & \xmark & \cmark & & \xmark & \cmark & \cmark & \xmark  & 
  							\begin{minipage}[t]{0.1\textwidth}
	CommNet
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.2\textwidth}

	 60.43\% 
  \end{minipage}	\\
  \hline

\hline Att $k^2$-trees  \citep{alvarez2018compact} & \cmark & \cmark & \cmark & \xmark & 
\begin{minipage}[t]{0.1\textwidth}
  			Étiqueté\\
  			Attribué\\
  			Multiple
  \end{minipage}	
& \xmark & \cmark & \cmark & \xmark  & 
  							\begin{minipage}[t]{0.15\textwidth}
	Movielen-10M
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.2\textwidth}

	 89.97\% 
  \end{minipage}	\\
  \hline

\hline dynAtt $k^2$-trees  \citep{alvarez2018compact} & \cmark & \cmark & \xmark & \cmark & 
\begin{minipage}[t]{0.1\textwidth}
  			Étiqueté\\
  			Attribué\\
  			Multiple
  \end{minipage}	
& \xmark & \cmark & \cmark & \xmark  & 
			\begin{minipage}[t]{0.1\textwidth}
	Movielen-10M
  \end{minipage}	
										 &
	\begin{minipage}[t]{0.2\textwidth}

	93.75\% 
  \end{minipage}	\\  				
  				\hline

@@
